The Social Conditioning of Fear

### 2023-12-06 scripts/manuscript.qmd
inline code requirement fulfilled

-   **sexornt**: Which of the following best describes you? [1] "Gay, lesbian, or homosexual" [2] Bisexual [3] Heterosexual or straight [99] "Refused"

@@

In the absence of running models, in this section we will discuss descriptive statistics through a series of tables and plots. We seek to show how the experience of fear differed across different measures of individual-level and community-level characteristics. To begin with, across our sample of 2318 cases, mean fear was calculated at `mean_fear`.

>>>>

-   **sexornt**: Which of the following best describes you? \[1\] "Gay, lesbian, or homosexual" \[2\] Bisexual \[3\] Heterosexual or straight \[99\] "Refused"

@@

In the absence of running models, in this section we will discuss descriptive statistics through a series of tables and plots. We seek to show how the experience of fear differed across different measures of individual-level and community-level characteristics. To begin with, across our sample of 2318 cases, mean fear was calculated at `r mean(as.numeric(overall_fear$fear, na.rm=TRUE))`.
